Evolution of ORM Systems: Formal Foundations

### 2013-01-16 doc/description.tex
added description to functions

\paragraph{Get Property or Association}
\begin{align*}
	\mathbf{propertyByName} : Label \times Label \times Application \rightarrow Property \\
	propertyByName(l_c, l_p, a) = \inference{\exists c \in classes(a): name(c) = l_c \\ \wedge \exists p \in properties(c) : name(p) = l_p}{p} \\
	l_c, l_p \in Label, a \lhd Application
\end{align*}
\begin{align*}
	\mathbf{associationByName} : Label \times Label \times Application \rightarrow Association \\
	associationByName(l_c, l_a, a) = \inference{\exists c \in classes(a): name(c) = l_c \\ \wedge \exists o \in associations(c) : name(o) = l_a}{o} \\
	l_c, l_a \in Label, a \lhd Application
\end{align*}

@@

\paragraph{Compare Tables} The need to compare two tables during the evolution results into the comparing operator $\cong$. The operator has to be defined for columns and foreign keys too.
\begin{align*}
	\mathbf{\cong} : Table \times Table \rightarrow Boolean \\
	t_1 \cong t_2 = \begin{cases}
 		\inference{|columns(t_1)| = |columns(t_2)| \\ \wedge |foreignKeys(t_1)| = |foreignKeys(t_2)| \\ \wedge \forall c \in columns(t_1) \exists e \in columns(t_2) : c = e \\ \wedge \forall f \in foreignKeys(t_1) \exists g \in foreignKeys(t_2) : f = g }{true}\\\\
 false
 \end{cases}\\
 t_1 \lhd Table, t_2 \lhd Table
\end{align*}
\begin{align*}
	\mathbf{\cong} : Column \times Column \rightarrow Boolean \\
	c_1 \cong c_2 = \begin{cases}
 		\inference{name(c_1) = name(c_2) \\ \wedge type(c_1) = type(c_2) \\ \wedge constraints(c_1) = comstraints(c_2)}{true}
 		\\ \\
		false
 \end{cases}\\
 c_1 \lhd Column, c_2 \lhd Column
\end{align*}
\begin{align*}
	\mathbf{\cong} : ForeignKey \times ForeignKey \rightarrow Boolean \\
	f_1 \cong f_2 = \begin{cases}
 		\inference{name(f_1) = name(f_2) \\ \wedge reference(f_1) = reference(f_2) \\ \wedge constraints(f_1) = comstraints(f_2}{true}
 		\\ \\
		false
 \end{cases}
\end{align*}

\paragraph{Find pair}
\begin{align*}
\mathbf{findPair} : Label \times Row \rightarrow Pair \\
	findPair(l, r) = \begin{cases}
		\inference{\exists p \in pairs(r) : reference(p) = l}{p} \\ \\
			\varnothing
		\end{cases}\\
		l \in Label, r \lhd Row
\end{align*}

@@

\paragraph{Alter Table}
\begin{align*}
alterTable:  Label \times Label \times Database \rightarrow Database \\
alterTable(l_o, l_n, d) = \inference{\exists t \in tables(d) : name(d) = l_o \\ \wedge \forall e \in tables(d) : name(e) \neq l_n}{\begin{gathered}
t.name = l_n \\ \wedge \forall e \in tables(a) \wedge \forall (f \in fks(e) \wedge reference(f) = l_o ) \\ : f.reference = l_n 
\end{gathered}}\\
l_o, l_n \in Label, s \in States, a \lhd Applications, d \lhd Database
\end{align*}

@@

\paragraph{Copy rows}
\begin{align*}
	\mathbf{copyRows} : Label \times Label \times (Row \times Row) \times Database \rightarrow Database \\
	copyRows(l_s, l_t, f_m, d) = \begin{cases}
 	\inference{|f_m| = \varnothing}{d} \\\\
 	\inference{|f_m| = 1 \\ \wedge \exists t_s, t_t \in tables(d) : name(t_s) = l_s, name(t_t) = l_t \\ \wedge t_s \cong t_t }{data(d) \cup insertRow(changeRef(l_t, first(f_m)), d)} \\\\
 	\inference{|f_m| > 1}{\begin{gathered}
		 d \bullet copyRows(l_s, l_t, head(f_m)) \bullet copyRows(l_s, l_t, tail(f_m))
	\end{gathered}}
  \end{cases} \\
  l_s, l_t \in Label, d \lhd Database
\end{align*}

\paragraph{Change ref}
\begin{align*}
	\mathbf{changeRef} : Label \times Row \rightarrow Row \\
	changeRef(l, r) = \inference{}{reference(r) = l } \\
	l \in Label, r \lhd Row
\end{align*}

\paragraph{Remove table}
\begin{align*}
	dropTable(l,d) = \inference{ \exists t \in tables(d) : name(t) = l  \\ \wedge \not \exists r \in data(d) : owningTable(r) = l \\  \not \exists j \in tables(d) \wedge f \in foreignKeys(j) : reference(f) = l }{ tables(d) \setminus \rho(c)}
\end{align*}

\paragraph{Remove column}
\begin{align*}
	dropColumn(l, l_p, d) = \inference{ \exists t \in tables(d) : name(t) = l \\ \wedge \exists c \in columns(t) : name(c) = l_p \\ \wedge \forall e \in  pairs(r), r \in tableData(t, d) : \\ reference(e) \neq l_p \vee value(e) = \varnothing  }{columns(t) \setminus c}\\
	 l \in Label, d \lhd Database 
\end{align*}

\paragraph{Remove Foreign Key}
\begin{align*}
	dropKey(l, l_p, d) = \inference{ \exists t \in tables(d) : name(t) = l \\ \wedge \exists c \in foreignKeys(t) : name(c) = l_p \\ \wedge \forall e \in  pairs(r), r \in tableData(t, d) : \\ reference(e) \neq l_p \vee value(e) = \varnothing  }{foreignKeys(t) \setminus c}\\
	 l \in Label, d \lhd Database 
\end{align*}

@@

\begin{align*}
\mathbf{addAsociation} : Label \times Association \times (Row \times Row) \times State \rightarrow State \\
\Psi(s, addAsociation(l, a, f_m)) = application(s) \circ addAssoc(l, a) \\
\Phi(s, addAsociation(l, a, f_m)) = database(s) \bullet insertAssoc(l, a, f_m)
\end{align*}

Adding an association into a database is complicated because of already existing instances. When an association between classes is added the instances of both classes has to be paired. This pairing is provided by the function $f_m$:
$$f_m : \rightarrow Instance \times Instance $$

\textbf{TODO: define the features of the $f_m$ function}

The $insertAssoc$ function is defined as:
\begin{align*}
insertAssoc : Association \times Database \times (Row \times Row) \\
insertAssoc(a, d, f_m) = \begin{cases}
\inference{ \exists t_s, t_t \in tables(d) : name(t_s) = name(owningClass(a)) \\ \wedge name(t_t) = reference(a) \\ \wedge \not \exists f \in foreignKeys(t_t) : name(f) = name(a) \\ startCardinality(a) \leq 1}{\begin{gathered}
addForeignKey(name(t_s), \rho(a,d), d) \\ \bullet \forall r \in f_m(owningClass(a), reference(a)) : \\ insertRow(row(name(t_s), [name(a), \\ value(primaryKey(first(r)))]), d)
\end{gathered}
 }
 \\ \\
\inference{ \exists t_s, t_t \in tables(d) : name(t_s) = name(owningClass(a)) \\ \wedge name(t_t) = reference(a) \\ \wedge \not \exists f \in foreignKeys(t_t) : name(f) = name(a) \\ startCardinality(a) > 1}{\begin{gathered} addTable(\rho(a,d),d) \\ \bullet \forall r \in f_m(owningClass(a), reference(a)),\\ t \in tables(d) : name(t) = name(a) : \\ insertRow(row(name(a), [name(t_s), \\ value(primaryKey(first(r)))] [name(t_t), \\ value(primaryKey(second(r)))]), d)
\end{gathered}
 } 
 \end{cases}\\
 a \in Associations, d \lhd Database
\end{align*}

@@

\subsection{Software Decomposition}
\begin{align*}
	\mathbf{RemoveClass}: Label \times Software \rightarrow State  \\
	\Psi RemoveClass(l, s) = applications(s) \circ remClass(l) \\
	\Phi RemoveClass(l, s) = database(s) \bullet dropTable(l) \\
	l \in Label, s \in Software 
\end{align*}

\begin{align*}
	\mathbf{RemoveProperty} : Label \times Label \times State \rightarrow State \\
	\Psi RemoveProperty(l, l_p, s) =  applications(s) \circ  remProp(l, l_p) \\
	\Phi RemoveProperty(l, l_p, s) = \begin{cases}
		 \inference{cardinality(propertyByName(l_p, application(s)) \leq 1}{database(s) \bullet dropColumn(l, l_p)}  \\\\
		 \inference{cardinality(propertyByName(l_p, application(s)) >1}{database(s) \bullet dropTable(l)}
 	\end{cases}\\
 	l, l_p \in Label, s \lhd Software
\end{align*}

\begin{align*}
    \mathbf{RemoveAssociation} : Label \times Labels \times State \rightarrow State \\ 
    \Psi RemoveAssociation(l, l_a, s) = application(s) \circ remAss(l, l_a) \\
    \Phi RemoveAssociation(l, l_a, s) = \begin{cases}
     	\inference{a = associationByName(l, l_a, application(s)) \\ \wedge startCardinality(a) \leq 1 \\}{database(s) \bullet dropForeignKey(l_a, reference(a))} \\\\
     	\inference{a = associationByName(l, l_a, application(s)) \\ \wedge startCardinality(a) > 1}{database(s) \bullet dropTable(l_a)} 
     \end{cases}\\
    l_c, l_a \in Labels, s \lhd Software
\end{align*}

\subsection{Software Alternation}
\paragraph{Rename Class}
\begin{align*}
\mathbf{RenameClass} : Label \times Label \times State \rightarrow State \\ 
\Psi(RenameClass(l_o, l_n), s) = application(s) \circ renClass(l_o, l_n) \\
\Phi(RenameClass(l_o, l_n), s) = database(s) \bullet alterTable(l_o, l_n) \\ \\
\end{align*}

\paragraph{Rename Property}
\begin{align*}
	\mathbf{RenameProperty} : Label \times Label \times Label \times State \rightarrow State \\ \\
\Psi(RenameProperty(l_c, l_o, l_n, s)) = application(s) \circ renProp(l_c, l_o, l_n) \\
\Phi(RenameProperty(l_c, l_o, l_n, s)) = \begin{cases}
 	\inference{cardinality(propertyByName(l_c, l_o, application(s))) \leq 1}{database(s) \bullet alterColumn(l_c, l_o, l_n))} \\\\
 	\inference{cardinality(propertyByName(l_c, l_o, application(s))) > 1}{database(s) \bullet alterTable(l_o, l_n, database(s))}
 \end{cases}\\
l_c, l_o, l_n \in Label,  s \lhd Software
\end{align*}

\paragraph{Rename Association}
\begin{align*}
\mathbf{RenameAssociation} : Label \times Label \times Label \times State \rightarrow State \\
\Psi(RenameAssocaiation(l_c, l_o, l_n), s) = application(s) \circ renAssoc(l_c, l_o, l_n)\\
\Phi(RenameAssocaiation(l_c, l_o, l_n), s) = \begin{cases}
	\inference{\exists a  \in associationByName(application(s)) : \\
  name(a) = l_c \\ \wedge startCardinality(a) > 1 }{database(s) \bullet alterTable(l_c, l_o, l_n)}
 \\ \\
  \inference{\exists a  \in associationByName(application(s)) : \\
  name(a) = l_c \\ \wedge startCardinality(a) \leq 1 }{\begin{gathered}
database(s) \\ \bullet alterForeignKey(endClass(a) ,l_c, l_o, l_n)
\end{gathered}}
 \end{cases}
\\\\
%	alterAssoc(l_c, l_o, l_n, d) = \begin{cases}
%?? \inference{\exists t \in tables(a) : name(t) = l_c \\ \wedge \exists f \in fks(t) : name(c) = l_o \\ \wedge \forall e \in fks(t) : name(e) \neq l_n}{\begin{gathered}
%f.name = l_n 
%\end{gathered}}
%\\ \\
%\inference{\exists t \in tables(a) : name(t) = l_o \\ \wedge \forall e \in tables(t) : name(e) \neq l_n}{\begin{gathered}
%t.name = l_n 
%\end{gathered}}
% \end{cases}
% \\
l_c, l_o, l_n \in Label, a \lhd Applications, s \in Sates, d \lhd Database
\end{align*}

>>>>

\paragraph{Get Property or Association} Functions $findProperty$ and $findAssociation$ returns a property (association) if it exists in given context - application and class of provided name.
\begin{align*}
	\mathbf{findProperty} : Label \times Label \times Application \rightarrow Property \\
	findProperty(l_c, l_p, a) = \inference{\exists c \in classes(a): name(c) = l_c \\ \wedge \exists p \in properties(c) : name(p) = l_p}{p} \\
	l_c, l_p \in Label, a \lhd Application
\end{align*}
\begin{align*}
	\mathbf{findAssociation} : Label \times Label \times Application \rightarrow Association \\
	findAssociation(l_c, l_a, a) = \inference{\exists c \in classes(a): name(c) = l_c \\ \wedge \exists o \in associations(c) : name(o) = l_a}{o} \\
	l_c, l_a \in Label, a \lhd Application
\end{align*}

@@

\paragraph{Compare} The need to compare two tables during the evolution results into the comparing operator $\cong$. The operator has to be defined for columns and foreign keys too.
\begin{align*}
	\mathbf{\cong} : Table \times Table \rightarrow Boolean \\
	t_1 \cong t_2 = \begin{cases}
 		\inference{|columns(t_1)| = |columns(t_2)| \\ \wedge |foreignKeys(t_1)| = |foreignKeys(t_2)| \\ \wedge \forall c \in columns(t_1) \exists e \in columns(t_2) : c = e \\ \wedge \forall f \in foreignKeys(t_1) \exists g \in foreignKeys(t_2) : f = g }{true}\\\\
 false
 \end{cases}\\
 t_1 \lhd Table, t_2 \lhd Table
\end{align*}
\begin{align*}
	\mathbf{\cong} : Column \times Column \rightarrow Boolean \\
	c_1 \cong c_2 = \begin{cases}
 		\inference{name(c_1) = name(c_2) \\ \wedge type(c_1) = type(c_2) \\ \wedge constraints(c_1) = comstraints(c_2)}{true}
 		\\ \\
		false
 \end{cases}\\
 c_1 \lhd Column, c_2 \lhd Column
\end{align*}
\begin{align*}
	\mathbf{\cong} : ForeignKey \times ForeignKey \rightarrow Boolean \\
	f_1 \cong f_2 = \begin{cases}
 		\inference{name(f_1) = name(f_2) \\ \wedge reference(f_1) = reference(f_2) \\ \wedge constraints(f_1) = comstraints(f_2}{true}
 		\\ \\
		false
 \end{cases}
\end{align*}

\paragraph{Find pair} The function returns a pair corresponding to given column (or key) name in concrete row.
\begin{align*}
\mathbf{findPair} : Label \times Row \rightarrow Pair \\
	findPair(l, r) = \begin{cases}
		\inference{\exists p \in pairs(r) : reference(p) = l}{p} \\ \\
			\varnothing
		\end{cases}\\
		l \in Label, r \lhd Row
\end{align*}

@@

\paragraph{Alter Table} The $alterTable$ function renames a table in  the database.
\begin{align*}
alterTable:  Label \times Label \times Database \rightarrow Database \\
alterTable(l_o, l_n, d) = \inference{\exists t \in tables(d) : name(d) = l_o \\ \wedge \forall e \in tables(d) : name(e) \neq l_n}{\begin{gathered}
t.name = l_n \\ \wedge \forall e \in tables(a) \wedge \forall (f \in fks(e) \wedge reference(f) = l_o ) \\ : f.reference = l_n 
\end{gathered}}\\
l_o, l_n \in Label, s \in States, a \lhd Applications, d \lhd Database
\end{align*}

@@

\paragraph{Copy rows} The function $copyRows$ creates a copy of a source table content in another table with the same structure. 
\begin{align*}
	\mathbf{copyRows} : Label \times Label \times (Row \times Row) \times Database \rightarrow Database \\
	copyRows(l_s, l_t, f_m, d) = \begin{cases}
 	\inference{|f_m| = \varnothing}{d} \\\\
 	\inference{|f_m| = 1 \\ \wedge \exists t_s, t_t \in tables(d) : name(t_s) = l_s, name(t_t) = l_t \\ \wedge t_s \cong t_t }{data(d) \cup insertRow(row(l, pairs(first(f_m))), d)} \\\\
 	\inference{|f_m| > 1}{\begin{gathered}
		 d \bullet copyRows(l_s, l_t, head(f_m)) \bullet copyRows(l_s, l_t, tail(f_m))
	\end{gathered}}
  \end{cases} \\
  l_s, l_t \in Label, d \lhd Database
\end{align*}

\paragraph{Remove table} The function removes a table if there are no stored data. This is because the data lost is undesirable in case of evolution. The consistency of foreign keys references has to be verified too.
\begin{align*}
	\mathbf{dropTable} : Label \times Database \rightarrow Database \\
	dropTable(l,d) = \inference{ \exists t \in tables(d) : name(t) = l  \\ \wedge \not \exists r \in data(d) : owningTable(r) = l \\  \not \exists j \in tables(d) \wedge f \in foreignKeys(j) : reference(f) = l }{ tables(d) \setminus \rho(c)}
\end{align*}

\paragraph{Remove column or foreign key} The situation is similar to the $dropTable$ function - there has to be no data in the column or key so it can be safely removed.
\begin{align*}
	\mathbf{dropColumn} : Label \times Label \times Database \rightarrow Database \\
	dropColumn(l, l_p, d) = \inference{ \exists t \in tables(d) : name(t) = l \\ \wedge \exists c \in columns(t) : name(c) = l_p \\ \wedge \forall e \in  pairs(r), r \in tableData(t, d) : \\ reference(e) \neq l_p \vee value(e) = \varnothing  }{columns(t) \setminus c}\\
	 l , l_p\in Label, d \lhd Database 
\end{align*}
\begin{align*}
	\mathbf{dropKey} : Label \times Label \times Database \rightarrow Database \\
	dropKey(l, l_p, d) = \inference{ \exists t \in tables(d) : name(t) = l \\ \wedge \exists c \in foreignKeys(t) : name(c) = l_p \\ \wedge \forall e \in  pairs(r), r \in tableData(t, d) : \\ reference(e) \neq l_p \vee value(e) = \varnothing  }{foreignKeys(t) \setminus c}\\
	 l, l_p \in Label, d \lhd Database 
\end{align*}

@@

\paragraph{Add association} Adding an association into a database is complicated because of already existing instances. When an association between classes is added the instances of both classes has to be paired. This pairing is provided by the function $f_m$:
$$f_m : \rightarrow Row \times Row $$

\textbf{TODO: define the features of the $f_m$ function}
\begin{align*}
\mathbf{addAsociation} : Label \times Association \times (Row \times Row) \times State \rightarrow State \\
\Psi(s, addAsociation(l, a, f_m)) = application(s) \circ addAssoc(l, a) \\
\Phi(s, addAsociation(l, a, f_m)) = database(s) \bullet insertAssoc(l, a, f_m)
\end{align*}
The $insertAssoc$ function is defined as:
\begin{align*}
insertAssoc : Association \times Database \times (Row \times Row) \\
insertAssoc(l, a, f_m, d) = \begin{cases}
\inference{ \exists t_s, t_t \in tables(d) : name(t_s) = l\\ \wedge name(t_t) = reference(a) \\ \wedge \not \exists f \in foreignKeys(t_t) : name(f) = name(a) \\ startCardinality(a) \leq 1}{\begin{gathered}
addForeignKey(name(t_s), \rho(a,d), d) \\ \bullet \forall r \in f_m(l, reference(a)) : \\ insertRow(row(name(t_s), [name(a), \\ value(primaryKey(first(r)))]), d)
\end{gathered}
 }
 \\ \\
\inference{ \exists t_s, t_t \in tables(d) : name(t_s) = l \\ \wedge name(t_t) = reference(a) \\ \wedge \not \exists f \in foreignKeys(t_t) : name(f) = name(a) \\ startCardinality(a) > 1}{\begin{gathered} addTable(\rho(a,d),d) \\ \bullet \forall r \in f_m(l, reference(a)),\\ t \in tables(d) : name(t) = name(a) : \\ insertRow(row(name(a), [name(t_s), \\ value(primaryKey(first(r)))] [name(t_t), \\ value(primaryKey(second(r)))]), d)
\end{gathered}
 } 
 \end{cases}\\
 a \in Associations, d \lhd Database
\end{align*}

@@

\subsection{Software Decomposition}
The removal of class, property or association is limited only by the constraints given in application or database transformations. The main constraint is there has to be no data, which can be lost during removal. 
\paragraph{Remove class}
\begin{align*}
	\mathbf{RemoveClass}: Label \times Software \rightarrow State  \\
	\Psi RemoveClass(l, s) = applications(s) \circ remClass(l) \\
	\Phi RemoveClass(l, s) = database(s) \bullet dropTable(l) \\
	l \in Label, s \in Software 
\end{align*}
\paragraph{Remove property}
\begin{align*}
	\mathbf{RemoveProperty} : Label \times Label \times State \rightarrow State \\
	\Psi RemoveProperty(l, l_p, s) =  applications(s) \circ  remProp(l, l_p) \\
	\Phi RemoveProperty(l, l_p, s) = \begin{cases}
		 \inference{cardinality(findProperty(l_p, application(s)) \leq 1}{database(s) \bullet dropColumn(l, l_p)}  \\\\
		 \inference{cardinality(findProperty(l_p, application(s)) >1}{database(s) \bullet dropTable(l)}
 	\end{cases}\\
 	l, l_p \in Label, s \lhd Software
\end{align*}
\paragraph{Remove association} 
\begin{align*}
    \mathbf{RemoveAssociation} : Label \times Labels \times State \rightarrow State \\ 
    \Psi RemoveAssociation(l, l_a, s) = application(s) \circ remAss(l, l_a) \\
    \Phi RemoveAssociation(l, l_a, s) = \begin{cases}
     	\inference{a = findAssociation(l, l_a, application(s)) \\ \wedge startCardinality(a) \leq 1 \\}{database(s) \bullet dropForeignKey(l_a, reference(a))} \\\\
     	\inference{a = findAssociation(l, l_a, application(s)) \\ \wedge startCardinality(a) > 1}{database(s) \bullet dropTable(l_a)} 
     \end{cases}\\
    l_c, l_a \in Labels, s \lhd Software
\end{align*}

\subsection{Software Alternation}
Alternation of a software is limited to renaming functions in our model.
\paragraph{Rename Class}
\begin{align*}
\mathbf{RenameClass} : Label \times Label \times State \rightarrow State \\ 
\Psi(RenameClass(l_o, l_n), s) = application(s) \circ renClass(l_o, l_n) \\
\Phi(RenameClass(l_o, l_n), s) = database(s) \bullet alterTable(l_o, l_n) \\ \\
\end{align*}

\paragraph{Rename Property}
\begin{align*}
	\mathbf{RenameProperty} : Label \times Label \times Label \times State \rightarrow State \\ \\
\Psi(RenameProperty(l_c, l_o, l_n, s)) = application(s) \circ renProp(l_c, l_o, l_n) \\
\Phi(RenameProperty(l_c, l_o, l_n, s)) = \begin{cases}
 	\inference{cardinality(findProperty(l_c, l_o, application(s))) \leq 1}{database(s) \bullet alterColumn(l_c, l_o, l_n))} \\\\
 	\inference{cardinality(findProperty(l_c, l_o, application(s))) > 1}{database(s) \bullet alterTable(l_o, l_n, database(s))}
 \end{cases}\\
l_c, l_o, l_n \in Label,  s \lhd Software
\end{align*}

\paragraph{Rename Association}
\begin{align*}
\mathbf{RenameAssociation} : Label \times Label \times Label \times State \rightarrow State \\
\Psi(RenameAssocaiation(l_c, l_o, l_n), s) = application(s) \circ renAssoc(l_c, l_o, l_n)\\
\Phi(RenameAssocaiation(l_c, l_o, l_n), s) = \begin{cases}
	\inference{\exists a  \in findAssociation(application(s)) : \\
  name(a) = l_c \\ \wedge startCardinality(a) > 1 }{database(s) \bullet alterTable(l_c, l_o, l_n)}
 \\ \\
  \inference{\exists a  \in findAssociation(application(s)) : \\
  name(a) = l_c \\ \wedge startCardinality(a) \leq 1 }{\begin{gathered}
database(s) \\ \bullet alterForeignKey(endClass(a) ,l_c, l_o, l_n)
\end{gathered}}
 \end{cases}
\\\\
%	alterAssoc(l_c, l_o, l_n, d) = \begin{cases}
%?? \inference{\exists t \in tables(a) : name(t) = l_c \\ \wedge \exists f \in fks(t) : name(c) = l_o \\ \wedge \forall e \in fks(t) : name(e) \neq l_n}{\begin{gathered}
%f.name = l_n 
%\end{gathered}}
%\\ \\
%\inference{\exists t \in tables(a) : name(t) = l_o \\ \wedge \forall e \in tables(t) : name(e) \neq l_n}{\begin{gathered}
%t.name = l_n 
%\end{gathered}}
% \end{cases}
% \\
l_c, l_o, l_n \in Label, a \lhd Applications, s \in Sates, d \lhd Database
\end{align*}
